\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[5][0pt]{ % 5th param optional spacing
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#2} & #3 \\
      \textit{\small#4} & \textit{\small #5} \\
    \end{tabular*}\vspace{#1} % <-- use optional spacing
}


\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}

\renewcommand{\baselinestretch}{0.98}
\small
\begin{document}

\begin{center}
    \textbf{\Huge \scshape Aman Kumar} \\ \vspace{1pt}
    \small \href{https://github.com/pirateking22017}{\underline{github.com/pirateking22017}} $|$ \href{mailto:theofficialakp@gmail.com}{\underline{theofficialakp@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/aman-padhy/}{\underline{linkedin.com/in/aman-padhy}}
\end{center}

\section{About Me}
\small{
I have always been driven by the desire to make (\& tinker with) things and solve problems, which is why I enjoy participating in hackathons and competitions that tackle real-world challenges. I also like mathematics and computer science.}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Maharashtra Institute of Technology, World Peace University}{2022-2026}
      {Bachelor of Technology in Computer Science and Engineering, Minor in Business Systems}{GPA 8.29/10}
    \vspace{-0.1cm} % tighten spacing

    \resumeSubheading
      {Army Public School, Pune}{2020-2021}
      {Class 12 (PCMB – Physics, Chemistry, Mathematics, Biology)}{Percentage: 95.4\%}
    \vspace{-0.1cm} % tighten spacing

    \resumeSubheading
      {Army Public School, Pune}{2018-2019}
      {Class 10 (Mathematics, Science, English)}{Percentage: 96.2\%}
  \resumeSubHeadingListEnd



\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Oracle Financial Services Software: Project Intern}{Jun 2025 – Aug 2025}
      {Pune, India}{}
      \resumeItemListStart
        \resumeItem{Offered a return full-time role at Oracle based on internship performance.}
        \resumeItem{Engineered an AI-driven assistant pipeline for Abort tool log dumps on Oracle Cloud Infrastructure with a RAG failsafe, reducing manual triage effort by 60\% and improving SRE resolution speed.}

        \resumeItem{Developed a Python-based tool to automate DR/DC server consistency checks, ensuring configuration alignment across environments and supporting RBI compliance by reducing manual validation time and improving reliability.}

        \resumeItem{Performed middleware integration and reliability testing on Oracle WebLogic-based services, validating API and transaction workflows across distributed systems.}
      \resumeItemListEnd

    \vspace{0.2cm} % <-- adjust this value as needed

    \resumeSubheading
      {Škoda Auto Volkswagen Training Academy - Product Development Intern}{Aug 2025 – Ongoing}
      {Pune, India}{}
      \resumeItemListStart
        \resumeItem{Designed and deployed ML-driven e-learning modules for sales training, leveraging Azure Cloud.}
        \resumeItem{Developed multimodal assessment systems integrating BERT-based NLP models, Azure Speech-to-Text DNNs, and Custom Vision CNNs to evaluate post-sales customer servicing.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd



\section{Projects}
  \resumeSubHeadingListStart
  \resumeProjectHeading
      {\textbf{Deep Reinforcement Learning for Basic Games} $|$ Deep Q-Networks, Double-DQN, Python, OpenAI Gym}{}
      \resumeItemListStart
        \resumeItem{Trained a Deep Reinforcement Learning agent that exceeds human-level performance on classic Atari games such as Pong, Breakout, and Boxing using raw game screen pixels as input.}
        \resumeItem{Analyzed and compared the performance of off-policy frameworks, including Deep Q-Network (DQN) and Double-DQN, to optimize learning efficiency and stability.}
      \resumeItemListEnd \vspace{0.2cm}
      
    \resumeProjectHeading
      {\textbf{Software Architecture – Commercia} $|$ Spring Boot, Angular, Kafka, Kubernetes, Grafana}{}
      \resumeItemListStart
        \resumeItem{Architected scalable microservices using Spring Boot and Kafka to handle high-volume transactions.}
        \resumeItem{Deployed on Kubernetes with auto-scaling and load balancing, ensuring fault-tolerance under stress.}
        \resumeItem{Built observability stack with Prometheus \& Grafana to monitor distributed workflows in real-time.}
      \resumeItemListEnd \vspace{0.2cm}
      \resumeProjectHeading
      {\textbf{Sports Analytics with YOLOv8 and OpenCV} $|$ Object Detection, Optical Flow, Perspective Transform, Python}{}
      \resumeItemListStart
        \resumeItem{Built a computer vision pipeline to detect players and track their movement in sports videos using YOLOv8.}
        \resumeItem{Segmented players with K-Means clustering to accurately identify t-shirt colors and applied optical flow to measure camera motion.}
        \resumeItem{Used OpenCV perspective transformation to analyze field depth, enabling computation of player speed and distance covered.}
        \resumeItemListEnd \vspace{-0.2cm} 
    \resumeProjectHeading
      {\textbf{Cloud Development – nextBlog} $|$ AWS, Amplify, Tailwind CSS, TipTap Editor}{}
      \resumeItemListStart
        \resumeItem{Developed a scalable blogging platform using Cognito, DynamoDB, S3, AppSync GraphQL}
        \resumeItem{Implemented modern UI/UX with seamless authentication and media management}
      \resumeItemListEnd \vspace{0.2cm}
    \resumeProjectHeading
      {\textbf{Modern Web Applications – Elsenote} $|$ Next.js 15, Lucia Auth, Prisma, Stream Chat}{}
      \resumeItemListStart
        \resumeItem{Developed a full-stack social platform with real-time chat, notifications, and optimized data-fetching.}
        \resumeItem{Implemented server-side rendering and caching for scalable performance using TanStack Query.}
      \resumeItemListEnd \vspace{0.2cm}
  \resumeSubHeadingListEnd


\section{Achievements}
\resumeSubHeadingListStart
  \resumeItem{\textbf{HackMIT – Winner (2025)}: Developed AstroFlow, a CSR pipeline tool for astrophotography using Real-ESRGAN and Vulkan (selected for MITWPU Incubator).}
  \resumeItem{\textbf{UBS Code for Good – 2nd Place (2025)}: Built RiseUp, an NGO upskilling platform using FrappeUI to boost user engagement. Offered an internship oppurtunity + Full time employment offer.}
  \resumeItem{\textbf{HackXMIT – Ideathon 2nd Place  (2025)}: Created Bib, a low-tech solution for delivering lessons to rural areas.}
  \resumeItem{\textbf{Smart India Hackathon – Internal Runner Up (2024)}: Built CyberFlow, a real-time cyber monitoring tool with AI/ML-driven incident detection.}
\resumeSubHeadingListEnd

\section{Extracurriculars}
\begin{itemize}[leftmargin=0.15in, label={}]
  \item \small{
    \textbf{Codeforces}{: Currently a Pupil (max score : 1201) } \\
     \textbf{Codechef}{: Currently a DIV4 (max score : 1256) }
  }
  \item \small{
    \textbf{Insight AI Club (Founding Member \& Tech Head \& Mentor)}{: Led a team of 120+ members; hosted 6+ workshops for 1000+ students on machine learning and cloud deployment. Mentored numerous juniors through projects and publications.}
  }
\end{itemize}

\section{Relevant Coursework}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
 \textbf{Computer Science}{: Data Structures \& Algorithms, Cloud Computing, Distributed Systems, Operating Systems, Database Systems, Software Architecture, Microservices, AI Applications} \\
 \textbf{Mathematics}{: Probability, Optimization, Statistics, Discrete Mathematics}
}}
 \end{itemize}

\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
 \textbf{Languages}{: C, C++, SQL, TypeScript, Python, Shell, Java} \\
 \textbf{AI/ML}{: PyTorch, TensorFlow, OpenAI Gym (now Gymnasium), Langchain, YOLOv8, OpenCV, Scikit-learn} \\
 \textbf{Backend/DevOps}{: Spring Boot, Node.js, Docker, Kubernetes, Kafka, GraphQL, REST APIs} \\
 \textbf{Cloud/Distributed}{: AWS (EC2, S3, DynamoDB, Cognito, AppSync), Azure (Azure App service, Statice web apps, Azure AI (Speech, Vision, Language), Azure Virtual Machines), Oracle Cloud Infrastructure} \\
 \textbf{Frontend}{: React.js, Next.js, Angular, Tailwind CSS, Bootstrap} \\
}}
 \end{itemize}

\end{document}
